### 2022-03-25 paper3.tex
Final Draft before defense

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the COVID-19
pandemic. I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during COVID-19. Importantly, I
find a novel moderating effect of signal discordance, the contextual diversity
of signals received by an ego. In other words, if there is diversity in the
information received by an ego, contagion is less likely to occur. This article
is an important contribution to literature on diffusion and social networks, as
it shows that the contagion process cannot be not fully understood without
looking at the context of each exposure to a contagion within  within the range
of contagions one experiences.

Keywords: Social Networks, Social Norms, Health Behavior, Diffusion, Contagion

\hypertarget{background}{%
\section{Background}\label{background}}

After spreading around the world in a matter of months, the coronavirus
(COVID-19) became a leading cause of death in the United States. Although the
Centers for Disease Control and Prevention (CDC) \citeyearpar{centersfordiseasecontrolandpreventionHowProtectYourself2020} proposed several potential mitigation strategies, the method of mitigation that received the most national
attention is the call to stay-at-home and social distance for non-essential
workers. CDC officials and frontline health care professionals advise that the
best way to prevent exposure to the virus is to stay at home and avoid close
contact with people.

@@

\hypertarget{the-social-contagion-model}{%
\subsection{The Social Contagion Model}\label{the-social-contagion-model}}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  \emph{Hypothesis 1} Relatively higher local rates of infection will lead to increased time spent in residence and increase vaccination uptake
\end{enumerate}

\hypertarget{complex-contagion-and-discordance}{%
\subsection{Complex Contagion and Discordance}\label{complex-contagion-and-discordance}}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \emph{Hypothesis 2} increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  \emph{Hypothesis 3} the effect of signal direction on time spent in residence and vaccine uptake will be moderated by diversity in signals (discordance)
\end{enumerate}

@@

There is some evidence I can draw upon to support the associative diffusion
fraemwork. For instance, there is a central conflict between religious and
scientific ideologies which I theorize leads more religious counties to reject
the stay-at-home order and vaccines \citep{evansReligionScienceEpistemological2008}
because the associative diffusion of these behaviors pits public health
recommendations against religious ideologies.
Furthermore, as COVID-19 has become a politically polarizing issue \citep{ternullo22},
conservative ideology and a general mistrust of ``big government'' \citep{frank2007, gauchat2008} 
are likely to lead to resistance to the government and scientific guidance.

\hypertarget{data-and-methods}{%
\section{Data and Methods}\label{data-and-methods}}

@@

\hypertarget{stay-at-home-rates}{%
\subsection{Stay at Home Rates}\label{stay-at-home-rates}}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-1}}
\caption{Stay at Home Rates over Time}\label{fig:plot-google}
\end{figure}

@@

I utilize the likelihood of a friendship connection between counties
to create a county-level social network weighted by the probability of a tie.
Using this network and the two independent variables above, I examine how the
vaccination and stay-at-home rates of peer counties is contagious to the
ego-county. To do this, I first take the weighted average of each ego's network
signals using equation \eqref{eq:networksignal} where \texttt{x} denotes the
vaccination and stay-at-home rates of each alter county and \texttt{w} represents the
likelihood of a friendship connection between the ego county and each of their
alters, lagged by one week. This `signal' of norms gives us insight into the
coevolving contagion patterns of the new social norm being established. The
likelihood of friendship connection comes from the ``Social Connectedness Index''
\citep{Bailey2018, facebook20} which indexes the social links between geographies by
the likelihood of Facebook friends. It is an aggregated measure of Facebook
friendship connections between counties. It corresponds to ``the (relative)
probability that two arbitrary Facebook users across two geographies are friends
with each other.'' The data is available at various geographic aggregation
levels, such as U.S. zip codes or entire countries. However, data is only
available at one time point because Facebook has found that although there are
individual changes in friendship connections over time, the aggregate
statistical probabilities of friendship remain stable. This measure is based on
user-provided information and real-time location-service data gathered by
Facebook. Facebook data has been shown to be highly representative of the U.S.
population and Facebook friendship links largely represent real-world
friendships \citep{bailey_etal18, jones_etal13}. The data has been tested to show
how initial COVID-19 hotspots are related to subsequent virus spread to
non-hotspots, even after controlling for population density and geographic
distance \citep{Kuchler2020}.

@@

The second independent variable, \emph{Signal Discordance}, builds on the network
signal but looks specifically at the extent to which a given ego-network
receives diverse contagion signals. Based on the hypothesis that when the
majority of alters is in concordance with each other, the signal to the ego is
reinforced and more impactful on the ego, a high discordance coefficient is
indicative of diverse signals which may prevent any clear interpretation of a
norm developing, whereas a low discordance coefficient would indicate reinforced
signaling. I use the formula to calculate weighted standard deviations, (see equation
\eqref{eq:signaldiscordance}) to provide a metric of a diversity of signals. In
this formula, \texttt{x} denotes the vaccination and stay-at-home rates of each alter
county and \texttt{w} represents the likelihood of a friendship connection between the
ego county and each of their alters, lagged by one week. Furthermore, \(\bar{x}^*\)
represents the weighted mean.

@@

My analytic strategy proceeds in four steps. In Tables
\ref{tab:google-desc-table} (Stay-at-Home) and \ref{tab:vacc-desc-table}
(Vaccination Uptake), I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations across the two cases.
Then, in Tables \ref{tab:google-tab} - \ref{tab:vacc-tab}, I fit a series of
three linear mixed effects regression models using the nlme package in R
\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates and
Vaccination rates. Linear mixed effects models are a form of hierarchical linear
models that contain both random and fixed effects. These models treat the
dependent variables as continuous. The following strategies I will outline are
identical for both case studies. Models 1 through 3 address hypotheses 1 through
3 respectively. Each model utilizes normalized independent variables, i.e.
variables that have been centered and scaled to have a mean of 0 and standard
deviation 1. The first model is a baseline linear mixed effects model that
employs all basic controls to predict the dependent variable, allowing both
time-varying and county-level variables to predict the outcome. All variables
have fixed effects, meaning that the county-level exogenous effects are
controlled for when estimating the coefficient. In addition, models are
specified with a random intercept per county. The lme models are set with a
autoregressive correlation structure (\texttt{correlation\ =\ corAR1()}) to control for
temporally autocorrelated error structures; models are also optimized using
Nelder--Mead, quasi-Newton and conjugate-gradient algorithms for box-constrained
optimization and simulated annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}).
This first model will address Hypothesis 1. To test hypothesis 2, I estimate
model 2 which builds on model 1 by first introducing vaccination signal. Because
the signal varies by week, I estimate this model with an interaction between
week and signal. And finally, because signal may have divergent effects across
counties, I set a random effect for signal nested by county. A visual
representation of this interaction can be seen in Figures
\ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
elaborates on the previous model by introducing both a fixed effect for signal
discordance and an interaction term between signal and discordance. Figures
\ref{fig:plot-google-h3} and \ref{fig:plot-vacc-h3} depict just how signal and
discordance interact across these two cases.

@@

In Table \ref{tab:google-tab} and Figures \ref{fig:plot-google-h2} -
\ref{fig:plot-google-h3}, I present the elaboratory county-level models that
predict stay-at-home rates, or, time spent in residence. Model 1 addresses
hypothesis 1, that relatively higher local rates of infection will lead to
increased time spent in residence. This model's phi paramter is 0.933, which is
a good indicator that adjacent time points for each county are related and the
model is specified correctly (Finch, Bolin, and Kelley 2014). In this first model, many controls
have an impact on the outcome. For instance, when controlling for everything
else, the percent of GOP votes in 2016, the percentage of residents who identify
racially as White, and higher rates of unemployment increased the stay-at-home
rate while Searches for norms online seems to
have an effect on the outcome: searches for `Fox News' are associated with
decreased stay-at-home rates, while searching for both `Social Distancing' and
`Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
perceived threat of the virus, measured through COVID-19 case rates, were not
significantly related to stay-at-home rates in model 1. In other words, for
every 1 standard deviation increase in COVID-19 case rates, stay-at-home rates
actually decreased by
0.0003 (\emph{p} = 0.936),
a very small and insignificant effect. In this case, I fail to reject the null
hypothesis that relatively higher local rates of infection will lead to
increased time spent in residence.

Table \ref{tab:google-tab} Model 2 investigates Hypothesis 2, that increased
average time spent in residence (signal direction) from alters will have a
positive effect on stay-at-home rates for the ego-county. This model builds on
model 1 by adding in the variable for Movement Signal (see \protect\hyperlink{network-signal}{Network
Signal} for specifications). For every one standard deviation
increase in the average time spent in residence of the county alters, an ego tends to also increase its' own stay-at-home rate by
0.473
(\emph{p} \textless{} 0.001). I am therefore able to reject my null hypothesis for hypothesis
2, that an increased average time spent in residence (signal direction) from
alters will have a positive effect on time spent in residence for the
ego-county.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h2-1}}
\caption{Predicted Values of Stay at Home Rate by Movement Signal}\label{fig:plot-google-h2}
\end{figure}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h3-1}}
\caption{Predicted Values of Stay at Home Rate Moderated}\label{fig:plot-google-h3}
\end{figure}

Model 3 then adds the concept of Signal Discordance to investigate Hypothesis 3,
that the effect of signal direction on stay-at-home rates will be moderated by a
diversity in signals (\emph{discordance}). Many of the controls remain consistent
throughout the models, with the exception of `Social Distancing' Trend whose
effect has been completely mediated by the inclusion of signal discordance.
Importantly, signal discordance has a negative effect on stay-at-home rates,
where every one standard deviation increase in discordance lowers stay-at-home rates by
-0.101
(\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a
coefficient of a similar magnitude, with every one standard deviation increase
in discordance and signal resulting in
-0.092
lower rates of time spent in residence, indicating moderation. Figure
\ref{fig:plot-google-h3} illustrates the moderating effect that signal
discordance has on signal. Under high discordance, the social influence effect
is almost completely moderated because there is no clear story or norm forming.
However, under low discordance, the signal is condensed, allowing for social
influence to have an effect. Explicitly, if a county is receiving a wide array
of low and high signals, their stay at home rates won't be affected by social
contagion. When a signal is concentrated or in agreement, the theoretical effect
of movement signaling on the ego are the strongest. With this, I am able to
reject the null hypothesis of no relationship for hypothesis 3 and find that the
effect of signal direction on time spent in residence is moderated by diversity
in signals.

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
rates of infection will lead to increased vaccination uptake. In this first
model, we see various controls impacting vaccination rates. For instance, when
controlling for everything else, higher income areas lead to higher vaccination
uptake. On the other hand, counties with higher unemployment and higher votes
for Donald J. Trump in the 2020 election are associated with lower vaccination
rates. Interestingly, counties that search for Fox News are more likely to have
higher vaccination rates while those performing Google searches for information
about the vaccine are likely to have lower rates of vaccination. The test of
Hypothesis 1 also returns surprising results: every 1 standard deviation
increase in county COVID-19 case rates is expected to yield a -0.008 decrease in
vaccination rates. This may be due to time ordering or reverse causality, where
individuals in counties who have higher rates of vaccination are less likely to
take tests to COVID-19 infections because of the higher likelihood of
asymptomaticity. However, it is important to note that the Case Rate variable
actually becomes distorted with the addition of Vaccination Signal and
Vaccination Discordance in models 2 and 3. Distortion occurs when the direction
of a focal relationship reverses sign once a third (distorter) variable is
controlled, in this case, those related to signal. Therefore, the results of
hypothesis 1 are quite inconclusive.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h2-1}}
\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h2}
\end{figure}

Table \ref{tab:vacc-tab} model 2 tests the hypothesis 2 that increase vaccine
uptake by alters will have a positive effect on vaccine uptake for the
ego-county. The results are incredibly clear: seeing alter counties receiving
vaccines is associated with higher vaccination rates. Specifically, a 1 standard
deviation increase in vaccine signal, the average rate of vaccination of a
county's alters, is associated with a
0.854
percent increase of vaccination rates for the ego county. The strength of this
result leads me to reject the null hypothesis for hypothesis 2 and find that
increased average time spent in residence (signal direction) from alters will
have a positive effect on time spent in residence for the ego-county. The
interaction of vaccine signal can be seen in Figure \ref{fig:plot-vacc-h2}.
While the interaction is not as extreme as the results for Hypothesis 2 for
Stay-at-Home rates, there is still a distinction between high and low
vaccination signals over time. The slope for Higher Vaccination Signal is less
pronounced than Low Vaccination Signal. This is likely an artifact where some
counties vaccinated broadly early on, so their vaccination rate stays rather
constant in later weeks. However, overall, the message is clear: ego-counties
who `see' high levels of vaccinations among their alters have higher vaccination
rates; those who don't see that social norm forming are much less likely to
vaccinate.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h3-1}}
\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h3}
\end{figure}

Table \ref{tab:vacc-tab} Model 3 then models the moderation of signal direction
for vaccine uptake by diversity in signals (\emph{Discordance}). This is a second
test of Hypothesis 3, that the effect of signal direction on vaccine uptake will
be moderated by diversity in signals. The coefficients in model 3 are largely
consistent with model 2 and there is very little change in the magnitude
or significance of the coefficients. Vaccination signal maintains to have a positive
effect on the alter's vaccination rates, while vaccination discordance has a negative effect on vaccination rates, where every one standard deviation increase in discordance lowers rates by -0.072 (\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a coefficient of a similar magnitude, with every one standard deviation increase
in discordance \emph{and} signal resulting in 
lower rates of vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this
relationship, where there is slight moderation of the effect on vaccine signal
on vaccination rates. If a county receives consistently high signals, they are
more likely to have more residents vaccinated. If a county receives high but
inconsistent signals, they are still decently likely to raise vaccination rates
but to a lesser extent. While not as strong of moderation the the findings for
Stay-at-Home Rates for hypothesis 3, I also reject the null hypothesis and find
a moderation of the relationship between signal direction and vaccine uptake by
discordance.

>>>>

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health
recommendations to mitigate the COVID-19 pandemic. Using theories like
associative diffusion and the integrated theoretical framework of norms, I test
models of behavioral adaption to public health recommendations and patterns of
complex contagion (the need for repeated exposures to a something novel for it
to diffuse) using linear mixed effects models. These models show that complex
contagion is a valid framework for the social contagion of new norms during
COVID-19. Importantly, I find a novel moderating effect of signal discordance,
the contextual diversity of signals received by an ego. If there is diversity in
the information received by an ego, contagion is less likely to occur. This
paper shows that the contagion process cannot be not fully understood without
looking at the context of each exposure to a contagion within the range of
contagions one experiences.

Keywords: Social Networks, Complex Contagion, Social Norms, Health Behavior, Diffusion

\hypertarget{background}{\section{Background}\label{background}}

After spreading around the world in a matter of months, the coronavirus
(COVID-19) became a leading cause of death in the United States. Although the
Centers for Disease Control and Prevention (CDC)
\citeyearpar{centersfordiseasecontrolandpreventionHowProtectYourself2020}
proposed several potential mitigation strategies, the method of mitigation that
received the most national attention is the call to stay-at-home and social
distance for non-essential workers. CDC officials and front line health care
professionals advise that the best way to prevent exposure to the virus is to
stay-at-home and avoid close contact with people.

@@

\hypertarget{the-social-contagion-model}{\subsection{The Social Contagion Model}\label{the-social-contagion-model}}

@@

\begin{hyp2}[H\ref{hyp:infection}] \label{hyp:infection}
 Relatively higher local rates of infection will lead to increased time spent in residence and increase vaccination uptake
\end{hyp2}

\hypertarget{complex-contagion-and-discordance}{\subsection{Complex Contagion and Discordance}\label{complex-contagion-and-discordance}}

@@

\begin{hyp2}[H\ref{hyp:direction}] \label{hyp:direction}
Increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
\end{hyp2}

@@

\begin{hyp2}[H\ref{hyp:discordance}] \label{hyp:discordance}
The effect of signal direction on time spent in residence and vaccine uptake will be moderated by diversity in signals (discordance)
\end{hyp2}

@@

There is some evidence I can draw upon to support the associative diffusion
framework. For instance, there is a central conflict between religious and
scientific ideologies which I theorize leads more religious counties to reject
the stay-at-home order and vaccines
\citep{evansReligionScienceEpistemological2008} because the associative
diffusion of these behaviors pits public health recommendations against
religious ideologies. Furthermore, as COVID-19 has become a politically
polarizing issue \citep{ternullo22}, conservative ideology and a general
mistrust of ``big government'' \citep{frank2007, gauchat2008} are likely to lead
to resistance to the government and scientific guidance.

\hypertarget{data-and-methods}{\section{Data and Methods}\label{data-and-methods}}

@@

\hypertarget{stay-at-home-rates}{\subsection{Stay-at-Home Rates}\label{stay-at-home-rates}}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-1}}
\caption{Stay-at-Home Rates over Time}\label{fig:plot-google}
\end{figure}

@@

I utilize the likelihood of a friendship connection between counties to create a
county-level social network weighted by the probability of a tie. Using this
network and the two independent variables above, I examine how the vaccination
and stay-at-home rates of peer counties is contagious to the ego-county. To do
this, I first take the weighted average of each ego's network signals using
equation \eqref{eq:networksignal} where \texttt{x} denotes the vaccination and
stay-at-home rates of each alter county and \texttt{w} represents the likelihood
of a friendship connection between the ego county and each of their alters,
lagged by one week. This `signal' of norms gives us insight into the co-evolving
contagion patterns of the new social norm being established. The likelihood of
friendship connection comes from the ``Social Connectedness Index''
\citep{Bailey2018, facebook20} which indexes the social links between
geographies by the likelihood of Facebook friends. It is an aggregated measure
of Facebook friendship connections between counties. It corresponds to ``the
(relative) probability that two arbitrary Facebook users across two geographies
are friends with each other.'' The data is available at various geographic
aggregation levels, such as U.S. zip codes or entire countries. However, data is
only available at one time point because Facebook has found that although there
are individual changes in friendship connections over time, the aggregate
statistical probabilities of friendship remain stable. This measure is based on
user-provided information and real-time location-service data gathered by
Facebook. Facebook data has been shown to be highly representative of the U.S.
population and Facebook friendship links largely represent real-world
friendships \citep{bailey_etal18, jones_etal13}. The data has been tested to
show how initial COVID-19 hot spots are related to subsequent virus spread to
non-hot-spots, even after controlling for population density and geographic
distance \citep{Kuchler2020}.

@@

The second independent variable, \emph{Signal Discordance}, builds on the
network signal but looks specifically at the extent to which a given ego-network
receives diverse contagion signals. Based on Hypothesis \ref{hyp:discordance},
that when the majority of alters is in concordance with each other, the signal
to the ego is reinforced and more potent on the ego, a high discordance
coefficient is indicative of diverse signals which may prevent any clear
interpretation of a norm developing, whereas a low discordance coefficient would
indicate reinforced signaling. I use the formula to calculate weighted standard
deviations, (see equation \eqref{eq:signaldiscordance}) to provide a metric of a
diversity of signals. In this formula, \texttt{x} denotes the vaccination and
stay-at-home rates of each alter county and \texttt{w} represents the likelihood
of a friendship connection between the ego county and each of their alters,
lagged by one week. Furthermore, \(\bar{x}^*\) represents the weighted mean.

@@

My analytic strategy proceeds in four steps. In Tables
\ref{tab:google-desc-table} (Stay-at-Home) and \ref{tab:vacc-desc-table}
(Vaccination Uptake), I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations across the two cases.
Then, in Tables \ref{tab:google-tab} - \ref{tab:vacc-tab}, I fit a series of
three linear mixed effects regression models using the nlme package in R
\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates
and Vaccination rates. Linear mixed effects models are a form of hierarchical
linear models that contain both random and fixed effects. These models treat the
dependent variables as continuous. The following strategies I will outline are
identical for both case studies. Models 1 through 3 address hypotheses
\ref{hyp:infection} through \ref{hyp:discordance} respectively. Each model
utilizes normalized independent variables, i.e. variables that have been
centered and scaled to have a mean of 0 and standard deviation 1. The first
model is a baseline linear mixed effects model that employs all basic controls
to predict the dependent variable, allowing both time-varying and county-level
variables to predict the outcome. All variables have fixed effects, meaning that
the county-level exogenous effects are controlled for when estimating the
coefficient. In addition, models are specified with a random intercept per
county. The lme models are set with a autoregressive correlation structure
(\texttt{correlation\ =\ corAR1()}) to control for temporally autocorrelated
error structures; models are also optimized using Nelder--Mead, quasi-Newton and
conjugate-gradient algorithms for box-constrained optimization and simulated
annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}). This first model
will address Hypothesis \ref{hyp:infection}. To test Hypothesis
\ref{hyp:direction}, I estimate model 2 which builds on model 1 by first
introducing vaccination signal. Because the signal varies by week, I estimate
this model with an interaction between week and signal. And finally, because
signal may have divergent effects across counties, I set a random effect for
signal nested by county. A visual representation of this interaction can be seen
in Figures \ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
elaborates on the previous model by introducing both a fixed effect for signal
discordance and an interaction term between signal and discordance. Figures
\ref{fig:plot-google-h3} and \ref{fig:plot-vacc-h3} depict just how signal and
discordance interact across these two cases.

@@

In Table \ref{tab:google-tab} and Figures \ref{fig:plot-google-h2} -
\ref{fig:plot-google-h3}, I present the elaboratory county-level models that
predict stay-at-home rates, or, time spent in residence. Model 1 addresses
Hypothesis \ref{hyp:infection}, that relatively higher local rates of infection
will lead to increased time spent in residence. This model's phi parameter is
0.933, which is a good indicator that adjacent time points for each county are
related and the model is specified correctly (Finch, Bolin, and Kelley 2014). In
this first model, many controls have an impact on the outcome. For instance,
when controlling for everything else, the percent of GOP votes in 2016, the
percentage of residents who identify racially as White, and higher rates of
unemployment increased the stay-at-home rate while Searches for norms online
seems to have an effect on the outcome: searches for `Fox News' are associated
with decreased stay-at-home rates, while searching for both `Social Distancing'
and `Covid Conspiracy' tend to increase time spent in residence. Interestingly,
the perceived threat of the virus, measured through COVID-19 case rates, were
not significantly related to stay-at-home rates in model 1. In other words, for
every 1 standard deviation increase in COVID-19 case rates, stay-at-home rates
actually decreased by 0.0003 (\emph{p} = 0.936), a very small and insignificant
effect. In this case, I fail to reject the null hypothesis that relatively
higher local rates of infection will lead to increased time spent in residence.

Table \ref{tab:google-tab} Model 2 investigates Hypothesis \ref{hyp:direction},
that increased average time spent in residence (signal direction) from alters
will have a positive effect on stay-at-home rates for the ego-county. This model
builds on model 1 by adding in the variable for Movement Signal (see
\protect\hyperlink{network-signal}{Network Signal} for specifications). For
every one standard deviation increase in the average time spent in residence of
the county alters, an ego tends to also increase its' own stay-at-home rate by
0.473 (\emph{p} \textless{} 0.001). I am therefore able to reject my null
hypothesis for Hypothesis \ref{hyp:direction}, that an increased average time
spent in residence (signal direction) from alters will have a positive effect on
time spent in residence for the ego-county.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h2-1}}
\caption{Predicted Values of Stay-at-Home Rate by Movement Signal, Model 2}\label{fig:plot-google-h2}
\end{figure}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h3-1}}
\caption{Predicted Values of Stay-at-Home Rate Moderated by Discordance, Model 3}\label{fig:plot-google-h3}
\end{figure}

Model 3 then adds the concept of Signal Discordance to investigate Hypothesis
\ref{hyp:discordance}, that the effect of signal direction on stay-at-home rates
will be moderated by a diversity in signals (\emph{discordance}). Many of the
controls remain consistent throughout the models, with the exception of `Social
Distancing' Trend whose effect has been completely mediated by the inclusion of
signal discordance. Importantly, signal discordance has a negative effect on
stay-at-home rates, where every one standard deviation increase in discordance
lowers stay-at-home rates by -0.101 (\emph{p} \textless{} 0.001). The
interaction between signal and signal discordance have a coefficient of a
similar magnitude, with every one standard deviation increase in discordance and
signal resulting in -0.092 lower rates of time spent in residence, indicating
moderation. Figure \ref{fig:plot-google-h3} illustrates the moderating effect
that signal discordance has on signal. Under high discordance, the social
influence effect is almost completely moderated because there is no clear story
or norm forming. However, under low discordance, the signal is condensed,
allowing for social influence to have an effect. Explicitly, if a county is
receiving a wide array of low and high signals, their stay-at-home rates won't
be affected by social contagion. When a signal is concentrated or in agreement,
the theoretical effect of movement signaling on the ego are the strongest. With
this, I am able to reject the null hypothesis of no relationship for Hypothesis
\ref{hyp:discordance} and find that the effect of signal direction on time spent
in residence is moderated by diversity in signals.

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses Hypothesis \ref{hyp:infection}, that
relatively higher local rates of infection will lead to increased vaccination
uptake. In this first model, we see various controls impacting vaccination
rates. For instance, when controlling for everything else, higher income areas
lead to higher vaccination uptake. On the other hand, counties with higher
unemployment and higher votes for Donald J. Trump in the 2020 election are
associated with lower vaccination rates. Interestingly, counties that search for
Fox News are more likely to have higher vaccination rates while those performing
Google searches for information about the vaccine are likely to have lower rates
of vaccination. The test of Hypothesis \ref{hyp:infection} also returns
surprising results: every 1 standard deviation increase in county COVID-19 case
rates is expected to yield a -0.008 decrease in vaccination rates. This may be
due to time ordering or reverse causality, where individuals in counties who
have higher rates of vaccination are less likely to take tests to COVID-19
infections because of the higher likelihood of asymptomaticity. However, it is
important to note that the Case Rate variable actually becomes distorted with
the addition of Vaccination Signal and Vaccination Discordance in models 2 and
3. Distortion occurs when the direction of a focal relationship reverses sign
once a third (distorter) variable is controlled, in this case, those related to
signal. Therefore, the results of Hypothesis \ref{hyp:infection} are quite
inconclusive.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h2-1}}
\caption{Predicted Values of Vaccination Rate by Vaccination Signal, Model 2}\label{fig:plot-vacc-h2}
\end{figure}

Table \ref{tab:vacc-tab} model 2 tests the Hypothesis \ref{hyp:direction} that
increase vaccine uptake by alters will have a positive effect on vaccine uptake
for the ego-county. The results are incredibly clear: seeing alter counties
receiving vaccines is associated with higher vaccination rates. Specifically, a
1 standard deviation increase in vaccine signal, the average rate of vaccination
of a county's alters, is associated with a 0.854 percent increase of vaccination
rates for the ego county. The strength of this result leads me to reject the
null hypothesis for Hypothesis \ref{hyp:direction} and find that increased
average time spent in residence (signal direction) from alters will have a
positive effect on time spent in residence for the ego-county. The interaction
of vaccine signal can be seen in Figure \ref{fig:plot-vacc-h2}. While the
interaction is not as extreme as the results for Hypothesis \ref{hyp:direction}
for Stay-at-Home rates, there is still a distinction between high and low
vaccination signals over time. The slope for Higher Vaccination Signal is less
pronounced than Low Vaccination Signal. This is likely an artifact where some
counties vaccinated broadly early on, so their vaccination rate stays rather
constant in later weeks. However, overall, the message is clear: ego-counties
who `see' high levels of vaccinations among their alters have higher vaccination
rates; those who don't see that social norm forming are much less likely to
vaccinate.

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h3-1}}
\caption{Predicted Values of Vaccination Rate Moderated by Discordance, Model 3}\label{fig:plot-vacc-h3}
\end{figure}

Table \ref{tab:vacc-tab} Model 3 then models the moderation of signal direction
for vaccine uptake by diversity in signals (\emph{Discordance}). This is a
second test of Hypothesis \ref{hyp:discordance}, that the effect of signal
direction on vaccine uptake will be moderated by diversity in signals. The
coefficients in model 3 are largely consistent with model 2 and there is very
little change in the magnitude or significance of the coefficients. Vaccination
signal maintains to have a positive effect on the alter's vaccination rates,
while vaccination discordance has a negative effect on vaccination rates, where
every one standard deviation increase in discordance lowers rates by -0.072
(\emph{p} \textless{} 0.001). The interaction between signal and signal
discordance have a coefficient of a similar magnitude, with every one standard
deviation increase in discordance \emph{and} signal resulting in lower rates of
vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this relationship, where
there is slight moderation of the effect on vaccine signal on vaccination rates.
If a county receives consistently high signals, they are more likely to have
more residents vaccinated. If a county receives high but inconsistent signals,
they are still decently likely to raise vaccination rates but to a lesser
extent. While not as strong of moderation the the findings for Stay-at-Home
Rates for Hypothesis \ref{hyp:discordance}, I also reject the null hypothesis
and find a moderation of the relationship between signal direction and vaccine
uptake by discordance.
